Polynomial expansions of finite volume data in a cut cell context

### 2023-04-07 example/DomainDecomposition/EBCellMerge/hoeb_geometry_test/_doc/paper.tex
paper preliminaries pushed

\section
\end{document}

>>>>

\section{Computing Taylor coefficients}

Consider a finite volume grid where we know all geometric moments to
order $P$.   Given values of $<\psi>$ everwhere on the grid, we wish to
approximate the Taylor coefficients at a volume $\ibold$ given that we
know $\cn_\ibold = \{\jbold\}$, the set of $N_v$ closest neighbors of
the volume $\ibold$.   Using the Taylor expansion at each point gives
us $N_v$ equations for $C^p$
\begin{equation}
  V_\jbold <\psi>_\jbold = \sum\limits_{p < P} C^p_\ibold m^p_\jbold.
\end{equation}
Let's say there are $N_p$ Taylor coefficients.   We can force
$N_v > N_p$ by getting a large enough neighborhood.    This means that
we have an overdetermined system of the form
\begin{equation*}
M C = P 
\end{equation*}
where $M = \{\{m^{pi}_\jbold\}\}$ and $P= \{<\psi_\jbold>\}$.
Since the system is overdetermined, we can introduce a 
meaningful weighting matrix $W$ and solve
\begin{equation*}
WMC = WP.
\end{equation*}
Diagonal weighing matricies are common.  Typically, the equations for volumes near the
target volume receive higher weights.   Since these matricies are
(deliberately) not square, we approximate the solution using a
Moore-Penrose pseudo-inverse:
\begin{equation*}
C = ((WM)^T(WM))^{-1} (WM)^T P.
\end{equation*}
The matrix inversion at the heart of this  method requires that we
need know to what degree the matrix $A = (WM)^T(WM)$  is invertable.

\end{document}
